\papertitle

### 2021-03-08 source_separation/paper/paper.tex
Edit beginning of Experiments

	Targets are separated into four sub-targets. Each sub-target is independently orchestrated with a randomly assigned "sub-orchestra." These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods.

>>>>

	We test the effectiveness of five difference source separation methods, both supervised and unsupervised, on 300 custom made targets that are combinations of sounds from different databases. During testing, targets input to each source separation method, which outputs four sub-targets. Then each sub-target is independently orchestrated with a randomly assigned subset of the full orchestra. These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods.
